### 2019-03-27 outline/outline.tex
Add annotation style & common bibliography

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{enumitem}
\usepackage[format=plain, font=it]{caption}
\usepackage{mathpazo}
\usepackage{biblatex}

@@

\newpage
\section{Bibliography}
\begin{thebibliography}{6}
	\bibitem{Atkinson, Edwards} Atkinson, B., \& Edwards, D. (2018). Generic Pipelines Using Docker: The DevOps Guide to Building Reusable, Platform Agnostic CI/CD Frameworks. Berkeley, CA: Apress. doi:\\\texttt{https://doi.org/10.1007/978-1-4842-3655-0}
	\bibitem{Bosch} Bosch, J. (2014). Continuous Software Engineering. Cham: Springer International Publishing. doi:\\\texttt{https://doi-org.ezp1.lib.umn.edu/10.1007/978-3-319-11283-1.}
	\bibitem{Stackify} Continuous Delivery, Deployment \& Integration: 20 Key Differences. (2018, June 04). Retrieved from \\\texttt{https://stackify.com/continuous-delivery-vs-continuous-\\deployment-vs-continuous-integration}
	\bibitem{Shahin, Babar, Zhu} Shahin, M., Babar, M. A., \& Zhu, L. (2017). Continuous Integration, Delivery and Deployment: A Systematic Review on Approaches, Tools, Challenges and Practices. IEEE Access, 5, 3909-3943. doi:\\\texttt{10.1109/access.2017.2685629}
	\bibitem{Stahl} St\aa hl, D. (2017). Large Scale Continuous Integration and Delivery: Making Great Software Better and Faster. [Groningen]: University of Groningen.
	\bibitem{Stahl, Hallen, Bosch} St\aa hl, D., Hall\'{e}n, K., \& Bosch, J. (2016). Achieving traceability in large scale continuous integration and delivery deployment, usage and validation of the eiffel framework. Empirical Software Engineering, 22(3), 967-995. doi:\\\texttt{10.1007/s10664-016-9457-1}
\end{thebibliography}

>>>>

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{enumitem}
\usepackage{mathpazo}
\usepackage[hyphens,spaces,obeyspaces]{url}
\usepackage{apacite}

@@

\newpage
\section{Bibliography}
\nocite{*}
\bibliographystyle{apacite}
\bibliography{../bibliography}
